Stack Safety is a Security Property

### 2021-04-10 tex/main.tex
Comments and polishing

For example, \citet{DBLP:conf/sp/RoesslerD18} describe how to protect the stack
using tag-based \emph{micro-policies}~\citep{pump_oakland2015}.
Intuitively, memory cells within each stack frame are tagged with the
identity of
the function that owns the frame, and access to those locations is then gated
according to the function that is currently executing. Roessler and Dehon
explored a number of versions
of this basic idea, with different ways of identifying
functions and deciding exactly which accesses are allowed.  These alternatives
vary in their
efficiency and in the spatial and temporal precision of their security guarantees.
For example, their \emph{Depth Isolation} policy demands that a function
owns any
frame into which it writes; this seems simple and intuitively correct, but can be expensive to implement.
Conversely, their \emph{Lazy Tagging and Clearing} policy improves
performance by
allowing ``illicit'' writes to out-of-scope stack frames so long as the
written locations are not
subsequently read. The justification for this form of laziness is that any
genuinely dangerous writes will ultimately be
detected before they can affect program behavior. \bcp{Awkward transition here.} But we clearly need a
more formal foundation for
expressing, comparing and verifying these micro-policy security claims, as well as those of
other enforcement technologies.

@@

In this work, we take the (informal) definitions of WBCF and LSE as a starting point,
but choose a different approach to formalizing them, based on the
technical framework of language-based security~\citep{??}.  We define
trace-based properties of \emph{stepwise stack integrity} and \emph{stack confidentiality}.
In applying these security concepts, we treat each caller-callee pair as mutually distrustful
and view the caller as needing protection from the callee. \apt{Need more explanation of
  ``nesting'' and our novelty factor here? Also about domains??}
{\em Integrity} says that a caller's local data is protected from modification by its callee.
This is vital for local reasoning about the behavior of the caller.
{\em Confidentiality} states that a caller's data is protected
from being leaked into its callee, and also that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface that does not include the caller's
local state or the uninitialized portion of the stack.
Together, these properties (informally) capture LSE, as well as the ``temporal stack safety''
notion that data outside of live frames should be inaccessible (which LSE does not address).
We also give a simple trace-based formalization of WBCF, which is essential for keeping the
notions of ``caller' and ``callee'' sensible.

>>>>

\bcp{this paragraph seems a bit in the way at the moment: the previous
  paragraph has already motivated the need for a formal characterization, so
  why not just go straight on and talk about ours?  I propose moving it to,
  say, just before ``To illustrate...''  We can also then drop the awkward
  last sentence.}
}For example, \citet{DBLP:conf/sp/RoesslerD18} describe how to protect the stack
using tag-based \emph{micro-policies}~\citep{pump_oakland2015}.
Intuitively, memory cells within each stack frame are tagged with the
identity of
the function that owns the frame, and access to those locations is then gated
according to the function that is currently executing. Roessler and Dehon
explore alternative versions
of this basic idea, with different ways of identifying
functions and deciding exactly which accesses are allowed, varying in their
efficiency and in the spatial and temporal precision of their security
guarantees.
For example, their \emph{Depth Isolation} policy demands that a function
owns any
frame into which it writes; this seems simple and intuitively correct, but can be expensive to implement.
Conversely, their \emph{Lazy Tagging and Clearing} policy improves
performance by
allowing ``illicit'' writes to inaccessible stack frames so long as the
written locations are not
subsequently read. The justification for this form of laziness is that any
genuinely dangerous writes will ultimately be
detected before they can affect program behavior. \bcp{Awkward transition here.} But we clearly need a
more formal foundation for
expressing, comparing and verifying these micro-policy security claims, as well as those of
other enforcement technologies.

@@

\bcp{If we end up adopting my recent proposal for defining subtraces and
  separating WBCF, I think we can be a bit stronger here: We define stack
  safety in IFC terminology based on the same intuitions as their LSE, but
  we consider (and define) WBCF to be a separate thing---desirable, but
  distinct from safety.  (If we make this argument, we'll need to show an
  example of a program that is stack safe but doesn't have WBCF.)}In this
work, we take the (informal) definitions of WBCF and LSE as a starting
point, but choose a different approach to formalizing them, based on the
technical framework of language-based security~\citep{??}.  We define
trace-based properties of \emph{stepwise stack integrity} and \emph{stack confidentiality}.
In applying these security concepts, we treat each caller-callee pair as mutually distrustful
and view the caller as needing protection from the callee. \apt{Need more explanation of
  ``nesting'' and our novelty factor here? Also about domains??}
{\em Integrity} says that a caller's local data is protected from modification by its callee.
This is vital for local reasoning about the behavior of the caller.
{\em Confidentiality} states that a caller's data is protected
from being leaked into its callee, and also that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface that does not include the caller's
local state or the uninitialized portion of the stack.
Together, these properties (informally) capture LSE, as well as the ``temporal stack safety''
notion that data outside of live frames should be inaccessible (which LSE does not address).
We also give a simple trace-based formalization of WBCF, which is essential for keeping the
notions of ``caller' and ``callee'' sensible.
